Technology-based aids for people affected by Autism Spectrum Disorder (ASD)

### 2017-11-21 paper.tex
Fixed floating figures

\begin{figure}[h]
\centering
\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{task1.png}
\caption{Task 1 path following}
\label{fig:task1}
\end{minipage}
\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{task1_pT.png}
\caption{Task 1 pathLxT vs n of trials}
\label{fig:task1_pT}
\end{minipage}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width = .55\textwidth]{path.png}
\caption{Trials A and B for a \gls{td} child}
\label{path}
\end{figure}

@@

>>>>

\begin{figure}[t]
\centering
\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{task1.png}
\caption{Task 1 path following}
\label{fig:task1}
\end{minipage}
\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{task1_pT.png}
\caption{Task 1 pathLxT vs n of trials}
\label{fig:task1_pT}
\end{minipage}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width = .55\textwidth]{path.png}
\caption{Trials A and B for a \gls{td} child}
\label{path}
\end{figure}

@@

In this work they try to fulfill these lacks using a set of advanced technology tools, specifically a \textit{NAO Robot} (visible in \autoref{fig:nao_robot}) and a Perception Neuron Set of 32 sensors.

In their proposal, the robot will replace the therapist in the room.
The therapist would wear portable motion sensors giving him a partial control of the robot motion, and he would receive a visual and auditory stream from the robot. The therapist would also be able to talk to the child through the robot, by using a robotic voice.

\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{nao_robot.png}
\caption{Scheme of AVATAR system}
\label{fig:nao_robot}
\end{minipage}
\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{scores.png}
\caption{Structure of AVATAR platform}
\label{fig:scores}
\end{minipage}

The strength of this work is that the robot behavior can be adapted based on the degree of engagement of the child in the session.
Indeed, as the session starts, a low number of \gls{dof} are given to the robot, in order to makes the child imitate a set of very simple movements.
As the patient progresses in the engagement (we'll see later that this means take more points), more \gls{dof} are given to the robot, usually enabling disabled actuators, in order to increase the complexity of the movements.

During the whole process a heart-rate measuring band is worn by the partecipant, to monitor the partecipant's level of anxiety and stop or change the session whenever an intervention is required.

To monitor the actual movements performed by the child, a Microsoft Kinect is used.

The movements performed by the robot and imitated by the child are specifically selected to teach the child how to interact with other people and to improve his response to social stimolous.

During the session, points are given to the child as he progresses and performs the right movement at the right time.
The total score is given by the sum of three contributes:

\begin{LaTeXdescription}
	\item[Motion Score] Is relative to the goodness of the movement made by the patient to imitate the robot;
	\item[Attention Score] the child takes one point for each second he's looking at the robot’s face whenever the robot is asking him a question;
	\item[Response Score] for this score, points are given for the delay time between the moment in which the robot asks a question and moment in which the child start answering the questions.
	10 points are given for the first 10 seconds after the robot/therapist stops talking, and one point is subtracted for each second of delay.
\end{LaTeXdescription}

After 20 minutes of session therapy, results are collected.
This experiment has been done in five healthy male children and with three different type of interaction subject: an avatar programmed as said before, a pre-programmed robot and a therapist in a classical face-to-face session. Score has been collected for each type of interaction and the results are shown in \autoref{fig:scores}.

As we can see the performance of the avatar are initially almost equal to the ones of a pre-programmed robot, but along the session, child gets bored of the last one due to its repetitive movements and requirements, while the score with the avatar increases due to its continuous adaption to the child needs.
The scores collected with a real therapist are very lower at the beginning compared with the first two type of interaction and it increases along the session since the therapist adapts the requirements to the child needs.
